Reflections from reproductions

### 2024-08-15 pages/reflections.qmd
feat(reflections): add reflections from Huang 2019 and Lim 2020

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

<!-- TODO: Note whether it not it worked with latest versions/versions used, if the versions needed weren't provided. Explain the backdating v.s. not backdating stuff with R (but that might fall under providing the environment itself?) -->

@@

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

## Run time

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications

@@

@@

## All the required outputs are calculated

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

@@

## If not provided in the script, then clearly present all parameters in the paper

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ |

@@

## Easy to figure out how to use output table/s to create tables/figures

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

## Provide code to calculate results mentioned in the text (but no in tables/figures)

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@@

>>>>

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 |

@@

@huang_optimizing_2019 was an R model. As no versions were provided, I initially tried to create an environment with R and package versions that were prior to the article publication date. However, I had great difficulties implementing this with R, and never managed to successfully do this. This was related to:

* The difficulty of switching between R versions
* Problems in finding available/a source for specific package versions for specific versions or R

@lim_staff_2020: Provides major Python version, but chose minor and package versions based on article publication date.

@@

## Model is provided in a "runnable" format

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ |

@huang_optimizing_2019: The code provided was to run the model as part of a web application, but the paper was not focused on this application, but instead on specific model scenarios, so I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | 🟡 |

@@

@huang_optimizing_2019: Model was set up as a function, with many of the required parameters already set as inputs to that function.

@lim_staff_2020: Structure of provided code (model largely in functions) made it easier when making changes to run it programmatically. However, it wasn't all in functions, and the model itself was designed to run a single scenario, so I did need to change to a function that can call to easily vary parameters and run scenarios programmatically. <!-- TODO: Consider whether I have evaluated this correctly -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ |

@@

<!-- TODO: Double-check this is marked correctly for Huang... I think it is, as some were not hard coded but some were... potentialy could say partially... -->

@lim_staff_2020: Several parameters were hard coded

@@

@@

## Include sufficient comments in the code

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | ❌ | ✅ |

@huang_optimizing_2019: Would have benefitted from more comments, as it took some time to decipher and ensure I have correctly understood code as it uses lots of abbreviations.

@lim_staff_2020: Lots of comments in the code (including doc-string-style comments at the start of functions) that aided understanding of how it worked.

## Run time and memory usage

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* <!-- TODO: Check run time of Huang -->
* @lim_staff_2020: Add parallel processing

## For slow models, it's very important to state the expected run time

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!----> | <!----> | ❌ |

For long models with no statement, it can take a while to realise that it's not an error in the code or anything, but actually just a long run time! And hard to know how long to expect, and whether it is without the capacities of your machine and so on.

## For computationally expensive models, state memory usage, and potentially include alternatives for running it on machines without the capacity for it

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!----> | <!----> | <!----> |

@@

@huang_optimizing_2019: Set up a notebook to programmatically run the model scenarios. It took alot of work to modify and write code that could run the scenarios, and I often made mistakes in my interpretation for the implementation of scenarios, which could be avoided if code for those scenarios was provided.

@lim_staff_2020: Several parameters or scenarios were not incorporated in the code, and had to be added (e.g. with conditional logic to skip or change code run, removing hard-coding, adding parameters to existing).

@@

## All the required outputs are calculated/provided

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ❌ |

@@

@lim_staff_2020: The model script provided was only set up to provide results from days 7, 14 and 21. The figures require daily results, so I needed to modify the code to output that.

@@

## Include correct parameters in the script (even if just for one scenario)

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | ❌ |

@huang_optimizing_2019: The baseline model in the script did not match the baseline model in the paper, so had to modify parameters.

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ |

@huang_optimizing_2019: In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code. However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct.

@lim_staff_2020: For Figure 5, had to guess the value for `staff_per_shift`.

## If not provided in the script, then *clearly* present all parameters in the paper

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ |

@@

@huang_optimizing_2019: The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | <!----> | ❌ |

@@

## Understandable output tables

E.g. Easy to figure out how to use output table/s to create tables/figures.

@@

@huang_optimizing_2019: It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.

@lim_staff_2020: The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity. However, if seeds had been present, we would have been able to say with certainty. I did not feel I needed to add seeds during the reproduction to get the same results.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | <!--TODO--> |

<!--TODO: Lim 2020... I think from memory that this output tables  similar to the paper, but I then changed them as that format was difficult to compare/work with -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ |

@huang_optimizing_2019: Had to write code from scratch. For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this). It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these). It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code). <!-- TODO: Consider whether this should be split into another box (i.e. about providing the processing?) -->

@@

## Provide code to calculate in-text results

By "in-text results", I am referred to results that are mentioned in the text but not included in/cannot be deduced from any of the tables or figures.

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A |

@@

For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction.

<!-- TODO: Check if any of these should be above. e.g. might want to put simplicity in a same way as i put run time - as simplicity is not inherently required (its about focus of project partly) BUT it is really handy (and it is always a good principle to hold) -->
